### 2016-11-08 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Eds

```{r Figure 1}
subset
temp <- subset(dd,Age<15)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>0])
temp <- subset(temp,BirdID %in% keep)
temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

 mins <- tapply(temp$Agemonths,temp$BirdID,min)
 keep2 <- names(mins[mins <400])
 temp <- subset(temp,BirdID %in% keep2)

temp$Agemonths <- temp$Agemonths/12

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))
  annotate('text',x = 0,y = 3,label = 'A')

temp <- dd3

Fig1B <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 3,label = 'B')

@@

temp <- dd3
dd3
props <- tapply(dd3$DeltaRTLF,dd3$TimeDiff,mean)
propn <- tapply(dd3$DeltaRTLF,dd3$TimeDiff,length)
temp <- data.frame(props,propn,TimeDiff = as.numeric(names(props))/12) %>%
  subset(propn > 10)

Fig1D <- ggplot(temp,aes(y = props,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_abline(slope = 0,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 2,label = 'D')

pdf('Figures/Figure 1.pdf',
    width = 8,
    height = 7,
    paper = 'a4')
multiplot(Fig1A,Fig1B,Fig1C,Fig1D,layout=matrix(c(1,2,3,4),nrow=2,byrow=T))
dev.off()

@@

ys <- names(which(table(subset(dd,Ageclass == 'CH')$LayYear)>10))
temp <- subset(dd,LayYear %in% ys)
temp$Cohort <- factor(temp$LayYear)

Fig2A <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(method = 'lm',formula = y~log(x),se = F)
  annotate('text',x = 0,y = 1.3,label = 'A')

temp2 <- ddply(temp,
               .(Agemonths,Cohort),
               summarise,
               MedianRTL = mean(RTL))  %>%
  subset(Agemonths < 20)

Fig2B <- ggplot(temp2,aes(x = Agemonths,y = MedianRTL,col = Cohort))+
  xlab('Age (months)') +
  geom_line()+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

temp <- dd14

Fig4A <- ggplot(temp,
       aes(x = Agemonths,
           col = factor(SurvivedNext),
           y = RTL)) +
  ylab('RTL') + 
  xlab('Survival probability') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_smooth(method = 'lm')
  annotate('text',x = 17,y = 2.5,label = 'C')

@@

>>>>

```{r Figure 1}

Fig1A <- subset(dd,Age<15) %>%
  ddply(.(BirdID),
        mutate,
        nreps = length(RTL)) %>%
  subset(nreps>0) %>%
  subset(!duplicated(paste0(BirdID,Agemonths))) %>%
  transform(Agemonthsdec = Agemonths/12) %>%
  ggplot(aes(x = Agemonthsdec,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))
  annotate('text',x = 0,y = 3,label = 'A')

Fig1B <- ggplot(dd3,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 3,label = 'B')

@@

pdf('Figures/Figure 1.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig1A,Fig1B,Fig1C,layout=matrix(c(1,1,1,1,2,3),nrow=3,byrow=T))
dev.off()

@@

Fig2 <- ddply(dd,
               .(Agemonths,LayYear),
               summarise,
               meanRTL = mean(RTL),
               n = length(RTL))  %>%
  ddply(.(LayYear),
        mutate,
        nAges = length(meanRTL),
        minAge = min(Agemonths)) %>%
  subset(minAge == 1) %>%
  subset(n > 5) %>%
  transform(Cohort = factor(LayYear)) %>%
  ggplot(aes(x = Agemonths,y = meanRTL,col = Cohort))+
  xlab('Age (months)') +
  geom_point()+
  geom_line()+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

```{r Figure 4}
dd14$r <- sample(1:nrow(dd14),replace = F)
temp <- dd14[order(dd14$BirdID,dd14$r,decreasing = F),] %>%
  subset(!duplicated(BirdID)) %>%
  subset(Died == 1)

Fig4A <- ggplot(temp,
       aes(x = Sex,
           col = factor(SurvivedNext),
           y = RTL)) +
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_boxplot(notch=T)
  annotate('text',x = 17,y = 2.5,label = 'C')

@@

x <- subset(dd14,Fledged == 'Fledglings')

table(x$Sex,x$LayYear)

dd14$SexAge <- paste(dd14$Fledged,dd14$Sex)

ggplot(dd14,aes(x = Tarsus,y = RTL,col = SexAge))+
geom_smooth(method = 'lm')
